Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
Justified the longer paragraphs.
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1647 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\textbf{Joshua} is an open-source toolkit for parsing-based machine translation that is written in Java. The initial release of \joshua  \cite{joshua-wmt09} was a re-implementation of the Hiero system \cite{hiero-2007} and all its associated algorithms, including: chart parsing, $n$-gram language model integration, beam and cube pruning, and $k$-best extraction.  The \joshua 1.0 release also included re-implementations of suffix array grammar extraction \cite{lopez:2007:EMNLP-CoNLL2007,PBML-2010-Joshua-grammar-extraction}  and minimum error rate training \cite{och-mert,Zaidan2009}.  Additionally, it included parallel and distributed computing techniques for salability \cite{Joshua-old}.

@@

Reproducing other researchers' machine translation experiments is difficult because the pipeline is too complex to fully detail in short conference papers. We have put together a workflow framework for designing and running reproducible machine translation experiments using \joshua \cite{Schwartz-wmt10-pipline}. Each step in the machine translation workflow (data preprocessing, grammar training, MERT, decoding, etc) is modeled by a Make script that defines how to run the tools used in that step, and an auxiliary configuration file that defines the exact parameters to be used in that step for a particular experimental setup. Workflows configured using this framework allow a complete experiment to be run -- from downloading data and software through scoring the final translated results -- by executing a single Makefile.
This framework encourages researchers to supplement research publications with links to the complete set of scripts and configurations that were actually used to run the experiment. The Johns Hopkins University submission for the WMT10 shared translation task was implemented in this framework, so it can be easily and exactly reproduced.

>>>>

\joshua is an open-source toolkit for parsing-based machine translation that is
written in Java. The initial release of \joshua  \cite{joshua-wmt09} was
a re-implementation of the Hiero system \cite{hiero-2007} and all its
associated algorithms, including: chart parsing, $n$-gram language model
integration, beam and cube pruning, and $k$-best extraction.  The \joshua 1.0
release also included re-implementations of suffix array grammar extraction
\cite{lopez:2007:EMNLP-CoNLL2007,PBML-2010-Joshua-grammar-extraction} and
minimum error rate training \cite{och-mert,Zaidan2009}.  Additionally, it
included parallel and distributed computing techniques for salability \cite{Joshua-old}.

@@

Reproducing other researchers' machine translation experiments is difficult
because the pipeline is too complex to fully detail in short conference papers.
We have put together a workflow framework for designing and running
reproducible machine translation experiments using \joshua \cite{Schwartz-wmt10-pipline}.
Each step in the machine translation workflow (data preprocessing, grammar
training, MERT, decoding, etc) is modeled by a Make script that defines how to
run the tools used in that step, and an auxiliary configuration file that
defines the exact parameters to be used in that step for a particular
experimental setup. Workflows configured using this framework allow a complete
experiment to be run -- from downloading data and software through scoring the
final translated results -- by executing a single Makefile.

This framework encourages researchers to supplement research publications with
links to the complete set of scripts and configurations that were actually used
to run the experiment. The Johns Hopkins University submission for the WMT10
shared translation task was implemented in this framework, so it can be easily
and exactly reproduced.
